Supporting Information : Asymmetric tail association in extreme climatic events affects population-extinction risk

### 2019-10-14 SuppMat.Rmd
methods editing continued

---
title: "Supporting Information : Asymmetric tail-association in extreme climatic events affects population-extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1in,right=1in,top=1in,bottom=1in"

@@

# Generating matrix with extreme tail association  \label{extr_tail_dep}

For extreme tail-association algorithm, a $N \times n$ matrix, M was generated of independent 
standard-normal random draws (in general). <!--where $N = numsteps(=25) \times numsims(=10000)$ : only for 2d case-->
Then, each row of M was identified for a first set of modifications
randomly and independently with a 50\% chance; for those rows identified, every
element of the row was replaced with the absolute
value of the first element of the row (including the first element itself).
For other rows, every element in the row was replaced by the negative of 
its own absolute value. This produces right-tail dependent
matrix, normally distributed for each column. If left-tail 
dependent noise is desired, take the negative of the entire matrix.
Our [code](https://github.com/sghosh89/ERC/blob/master/ExtremeTailDep.R) for
generating extreme tail association matrix is flexible enough, so that 
matrix M can be generated initially with independent random draws from a normal 
distribution with a specified mean and standard deviation.

>>>>

---
title: "Supporting Information : Asymmetric tail association in extreme climatic events affects population-extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1in,right=1in,top=1in,bottom=1in"

@@

# A brief introduction about "copulas"  \label{intro_copula}

# Algorithm to generate extreme tail association  \label{extr_tail_dep}

For extreme tail association algorithm, a $N \times n$ matrix, M was generated of independent 
standard-normal random draws (in general). <!--where $N = numsteps(=25) \times numsims(=10000)$ : only for 2d case-->
Then, each row of M was identified for a first set of modifications
randomly and independently with a 50\% chance; for those rows identified, every
element of the row was replaced with the absolute
value of the first element of the row (including the first element itself).
For other rows, every element in the row was replaced by the negative of 
its own absolute value. This produces right-tail dependent
matrix, normally distributed for each column. If left-tail 
dependent noise is desired, take the negative of the entire matrix.
Our [code](https://github.com/sghosh89/ERC/blob/master/ExtremeTailDep.R) for
generating extreme tail association matrix is flexible enough, so that 
matrix M can be generated initially with independent random draws from a normal 
distribution with a specified mean and standard deviation.
